parental migration and adolescents educational performance

### 2023-06-09 analysis/Gu-thesis-script.Rmd
Update code, writing, bibliography

```{r Merge data}
d <- d_stu1 |> 
  left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) |>
  left_join(d_stu2, by=c('ids', 'schids', 'clsids', 'ctyids')) |>
  left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall')) 
```

@@

```{r Control variables}
d_cl <- d_cl |> mutate(
         child.age = 2013 - a02a, 
         child.is.girl = if_else(a01 == 2, 1, 0), 
         child.has.rural.hukou = sthktype, 
         child.in.boarding.school = stbrd, 
         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), 
         child.had.skipped.grade = if_else(c03 == 0, 0, 1), 
         child.had.repeated.grade = if_else(c04 == 0, 0, 1), 
         child.went.to.preschool = if_else(c01 == 1, 1, 0), 
         child.number.of.sibling = if_else(stonly == 1, 0, stsib),
         parent.has.white.collar.job = if_else(be08==1|be08==2|be08==3, 1, 0),
         home.economic.resource = steco_5c, 
         home.has.internet = if_else(b13 == 2, 1, 0), 
         home.extracurricular.book = b12 
) |> drop_na(
child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, child.number.of.sibling, 
parent.has.white.collar.job, 
home.has.internet, home.extracurricular.book, home.economic.resource)
```

```{r Mother education}
d_cl <- d_cl |> mutate(mother.education.level = NA)
d_cl$mother.education.level[d_cl$stmedu == 1|d_cl$stmedu == 2] <- 0 
d_cl$mother.education.level[d_cl$stmedu == 3] <- 1
d_cl$mother.education.level[d_cl$stmedu == 4|d_cl$stmedu == 5|d_cl$stmedu == 6] <- 2
d_cl$mother.education.level[d_cl$stmedu == 7] <- 3
d_cl$mother.education.level[d_cl$stmedu == 8] <- 4
d_cl$mother.education.level[d_cl$stmedu == 9] <- 5
```

```{r Father education}
d_cl <- d_cl |> mutate(father.education.level = NA)
d_cl$father.education.level[d_cl$stfedu == 1|d_cl$stfedu == 2] <- 0
d_cl$father.education.level[d_cl$stfedu == 3] <- 1
d_cl$father.education.level[d_cl$stfedu == 4|d_cl$stfedu == 5|d_cl$stfedu == 6] <- 2
d_cl$father.education.level[d_cl$stfedu == 7] <- 3
d_cl$father.education.level[d_cl$stfedu == 8] <- 4
d_cl$father.education.level[d_cl$stfedu == 9] <- 5
```

```{r Parent expectation}
d_cl <- d_cl |> mutate(parent.expectation = NA)
d_cl$parent.expectation[d_cl$ba18 == 1|d_cl$ba18 == 2] <- 1
d_cl$parent.expectation[d_cl$ba18 == 3|d_cl$ba18 == 4|d_cl$ba18 == 5] <- 2
d_cl$parent.expectation[d_cl$ba18 == 6] <- 3
d_cl$parent.expectation[d_cl$ba18 == 7] <- 4
d_cl$parent.expectation[d_cl$ba18 == 8|d_cl$ba18 == 9] <- 5
```

```{r Child aspiration}
d_cl <- d_cl |> mutate(child.education.aspiration = NA)
d_cl$child.education.aspiration[d_cl$c22 == 1|d_cl$c22 == 2|d_cl$c22 == 10] <- 1
d_cl$child.education.aspiration[d_cl$c22 == 3|d_cl$c22 == 4|d_cl$c22 == 5] <- 2
d_cl$child.education.aspiration[d_cl$c22 == 6] <- 3
d_cl$child.education.aspiration[d_cl$c22 == 7] <- 4
d_cl$child.education.aspiration[d_cl$c22 == 8|d_cl$c22 == 9] <- 5
```

@@

```{r}
d_cl <- d_cl |>  drop_na(
  mother.education.level, 
  father.education.level,
  parent.expectation, 
  child.health,
  #child.short.sighted,
  child.education.aspiration)
```

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl |> mutate(
  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became Migrated from household between baseline and endline survey
  migr_fa_only = NA,
  #migr_fa = NA,
  migr_mo_only = NA,
  #migr_mo = NA,
  migr_both = NA
  ) |> drop_na(migr)
```

Only mother migrated
```{r Any parent migrated}
d_cl <- d_cl |> mutate(
  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
  migr_fa_only = NA,
  migr_mo_only = NA,
  migr_both = NA
  ) |> drop_na(migr)
```

```{r Only mother migrated}
d_cl$migr_mo_only[d_cl$migr == 0] <- 0
d_cl$migr_mo_only[d_cl$w2ba0201==1 & d_cl$w2ba0202==0] <- 1 
```

```{r Only father migrated}
d_cl$migr_fa_only[d_cl$migr == 0] <- 0
d_cl$migr_fa_only[d_cl$w2ba0201==0 & d_cl$w2ba0202==1] <- 1 
```

```{r Both parents migrated}
d_cl$migr_both[d_cl$migr == 0] <- 0
d_cl$migr_both[d_cl$w2ba0201==0 & d_cl$w2ba0202==0] <- 1
```

## Descriptive statistics
```{r Cleaned data}
df <- d_cl |>
  select(
  migr, migr_mo_only, migr_fa_only, migr_both, schids, ctyids,
  w1cog_100, w2cog_100, w1avg_100, w2avg_100, cog_dif, avg_dif,
  child.age, child.number.of.sibling, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, parent.expectation, home.has.internet,
  child.health, child.education.aspiration, 
  mother.education.level, father.education.level, 
  home.extracurricular.book, home.economic.resource) 
```

@@

```{r Data for treatment variable summary}
d_idpvar <- df |> 
  select(migr:migr_both) |>
  mutate(`Parental Migration` = if_else(migr==1, 'Yes', 'No')) |>
  mutate(`Parental Migration Type` = NA) 
d_idpvar$`Parental Migration Type`[d_idpvar$migr==0] <- 'Both Parents at Home'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_mo_only==1] <- 'Only Mother Migrated'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_fa_only==1] <- 'Only Father Migrated'
d_idpvar$`Parental Migration Type`[d_idpvar$migr_both==1] <- 'Both Parents Migrated'
d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

```{r Treatment variable summary}
tab_idpvar <- st(
  data = d_idpvar,
  out = 'return'
)
tab_idpvar[tab_idpvar == 4114] <- ''
tab_idpvar
```

@@

```{r Data for binary control variable summary}
d_ctvar_dit <- d_migr |>
  select(`Parental Migration`,child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.had.skipped.grade, child.had.repeated.grade, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |> 
  mutate_all(as_factor)
```

```{r Binary control variable summary}
tab_ctvar_dit <- 
  st(
  data = d_ctvar_dit,
  digits = 2,
  group = 'Parental Migration',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = "return"
  )
tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
tab_ctvar_dit[tab_ctvar_dit == 3465|tab_ctvar_dit == 649] <- ''
tab_ctvar_dit 
```

```{r Data for categorical control variable summary}
d_ctvar_cnt <- d_migr |>
  select(`Parental Migration`, child.age, child.number.of.sibling, child.health, child.education.aspiration, 
  mother.education.level, father.education.level, parent.expectation, 
  home.extracurricular.book, home.economic.resource)
```

@@

```{r Data for categorical control variable measurement}
d_ctvar_label <- d_ctvar_cnt|>
  select(!(`Parental Migration`:child.number.of.sibling)) |> 
  add_value_labels(
    father.education.level = c(
     '0 = Primary school and below' = 0,
     '1 = Junior high school' = 1 ,
     '2 = Senior high school' = 2,
     '3 = Associate college' = 3,
     '4 = University' = 4,
     '5 = Postgraduate' = 5),
    mother.education.level = c(
     '0 = Primary school and below' = 0,
     '1 = Junior high school' = 1 ,
     '2 = Senior high school' = 2,
     '3 = Associate college' = 3,
     '4 = University' = 4,
     '5 = Postgraduate' = 5),
    child.education.aspiration = c(
     '1 = Junior high school' = 1 ,
     '2 = Senior high school' = 2,
     '3 = Associate college' = 3,
     '4 = University' = 4,
     '5 = Postgraduate' = 5),
    child.education.aspiration = c(
     '1 = Junior high school' = 1 ,
     '2 = Senior high school' = 2,
     '3 = Associate college' = 3,
     '4 = University' = 4,
     '5 = Postgraduate' = 5), 
    parent.expectation = c(
     '1 = Junior high school' = 1 ,
     '2 = Senior high school' = 2,
     '3 = Associate college' = 3,
     '4 = University' = 4,
     '5 = Postgraduate' = 5),
    home.economic.resource = c(
      '1 = Very poor' = 1,
      '2 = Somewhat poor' = 2,
      '3 = Moderate' = 3,
      '4 = Somewhat rich' = 4,
      '5 = Very rich' = 5),
    child.health = c(
      '1 = Very poor' = 1,
      '2 = Somewhat poor' = 2,
      '3 = Moderate' = 3,
      '4 = Good' = 4,
      '5 = Very good' = 5),
    home.extracurricular.book = c(
      '1 = Very few' = 1,
      '2 = Not many' = 2,
      '3 = Some' = 3,
      '4 = Quite a few' = 4,
      '5 = A great number' = 5),
    ) |>
  as_factor()
```

```{r Measurement for categorical control variable}
tab_var <- st(
  data = d_ctvar_label,
  out = 'return'
)
tab_var[tab_var == 4114] <- ''
tab_var
```

```{r Data for violin plots}
d_smr <- d_migr |> 
  mutate(`Parental Migration Type` = 0) 
d_smr$`Parental Migration Type`[d_smr$migr==0] <- 'Both Parents At Home'
d_smr$`Parental Migration Type`[d_smr$migr_mo_only==1] <- 'Only Mother'
d_smr$`Parental Migration Type`[d_smr$migr_fa_only==1] <- 'Only Father'
d_smr$`Parental Migration Type`[d_smr$migr_both==1] <- 'Both Parents'
d_smr <- d_smr |> select(!migr_mo_only & !migr_fa_only & !migr_both)
```

@@

```{r Adjusted regression on cognitive score}
did_adj_cog <- feols(cog_dif ~ migr + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df) 
did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df) 
did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df) 
did_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
```

```{r Adjusted regression on exam grade}
did_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df) 
did_adj_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df) 
did_adj_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df) 
did_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
```

@@

## Matching
```{r Match on any parent migration}
m.out <- matchit(
  migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = df, 
  ratio = 3,
  method = "optimal", 
  distance = "glm",
  exact= migr ~ ctyids
  )
```

@@

```{r Match on mother-only migration}
d_mo_only <- d_cl |> drop_na(migr_mo_only)
m.out_mo_only <- 
  matchit(migr_mo_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_mo_only, 
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact= migr_mo_only ~ ctyids
  )
```

@@

```{r Match on father-only migration}
d_fa_only <- d_cl |> drop_na(migr_fa_only)
m.out_fa_only <- matchit(
  migr_fa_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
  data = d_fa_only,
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact= migr_fa_only ~ ctyids
  )
```

@@

```{r Match on both parents migration}
d_both <- d_cl |> drop_na(migr_both) 
m.out_both <- matchit(
  migr_both ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + mother.education.level + father.education.level +  home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_both, 
  method = "optimal",
  distance = "glm",
  ratio = 3,
  exact= migr_both ~ ctyids
  )
```

@@

```{}
summary(m.out)
summary(m.out_mo_only)
summary(m.out_fa_only)
summary(m.out_both)
```

@@

```{r save image}
save.image('.RData')
```

>>>>

```{r Merge data}
d <- d_stu1 |> 
  left_join(d_par1, by=c('ids', 'schids', 'clsids', 'ctyids', 'fall')) |>
  left_join(d_stu2, by=c('ids', 'schids', 'clsids', 'ctyids')) |>
  left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall')) 
rm('d_stu1', 'd_stu2', 'd_par1', 'd_par2')
```

@@

```{r Control variables}
d_cl <- d_cl |> mutate(
         child.age = 
           if_else(
             fall == 1, 
             2014 - a02a - a02b/12, 
             2014 - a02a - a02b/12 + 0.5),
         child.is.girl = if_else(stsex == 1, 0, 1), 
         child.has.rural.hukou = sthktype, 
         child.in.boarding.school = stbrd, 
         child.is.ethnic.minority = if_else(a03 != 1, 1, 0), 
         child.went.to.preschool = if_else(c01 == 1, 1, 0), 
         child.number.of.sibling = if_else(stonly == 1, 0, stsib),
         home.economic.resource = steco_5c, 
         home.has.internet = if_else(b13 == 2, 1, 0), 
         home.extracurricular.book = b12 
)  
```

```{r Parent education}
d_cl <- d_cl |> mutate(
  parent.education.level = 
    case_when(
      stprhedu == 1|stprhedu == 2 ~ 0,
      stprhedu == 3 ~ 1,
      stprhedu == 4|stprhedu == 5|stprhedu == 6 ~ 2,
      stprhedu == 7 ~ 3,
      stprhedu == 8 ~ 4,
      stprhedu == 9 ~ 5)
)
```

```{r Parent expectation}
d_cl <- d_cl |> mutate(
  parexp = 
    if_else(
      is.na(ba18),
        b31,
        ba18)
) |> mutate(
  parent.expectation = 
    case_when(
      parexp == 10 ~ 0,
      parexp == 1|parexp == 2 ~ 1,
      parexp == 3|parexp == 4|parexp == 5 ~ 2,
      parexp == 6 ~ 3,
      parexp == 7 ~ 4,
      parexp == 8|parexp == 9 ~ 5
    )
)
```

```{r Parent job}
d_cl <- d_cl |> mutate(
  b08ch = if_else(
    b08a==1|b08a==2|b08a==3|b08b==1|b08b==2|b08b==3,
    1,
    0
  ),
  b08pr = 
    if_else(be08==1|be08==2|be08==3, 1, 0)
)
d_cl <- d_cl |> mutate(
  parent.has.white.collar.job = 
    if_else(
      is.na(b08ch),
      b08pr,
      b08ch
    )
)
```

```{r Child aspiration}
d_cl <- d_cl |> mutate(
  child.education.aspiration = 
    case_when(
      c22 == 10 ~ 0,
      c22 == 1|c22 == 2 ~ 1,
      c22 == 3|c22 == 4|c22 == 5 ~ 2,
      c22 == 6 ~ 3,
      c22 == 7 ~ 4,
      c22 == 8|c22 == 9 ~ 5
    )
)
```

@@

```{r Drop NA}
d_cl <- d_cl |>  drop_na(
  child.age, child.is.girl, child.has.rural.hukou, child.in.boarding.school, child.is.ethnic.minority, child.went.to.preschool, child.number.of.sibling, 
  #child.had.skipped.grade,
  #child.had.repeated.grade,
home.has.internet, home.extracurricular.book, home.economic.resource,
  #mother.education.level, 
  #father.education.level,
  parent.education.level,
  parent.expectation, 
  child.health,
  #child.short.sighted,
  child.education.aspiration)
```

## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r Any parent migrated}
d_cl <- d_cl |> mutate(
  migr = if_else(w2ba0201==0 | w2ba0202==0, 1, 0) #Any parent became absent from household between baseline and endline survey
  ) |> drop_na(migr)
```

```{r Only mother migrated}
d_cl <- d_cl |> 
  mutate(
    migr_mo_only = 
      case_when(
        w2ba0201==1 & w2ba0202==0 ~ 1,
        migr == 0 ~ 0,
        .default = NA
      )
  )
```

```{r Only father migrated}
d_cl <- d_cl |> 
  mutate(
    migr_fa_only = 
      case_when(
        w2ba0201==0 & w2ba0202==1 ~ 1,
        migr == 0 ~ 0,
        .default = NA
      )
  )
```

```{r Both parents migrated}
d_cl <- d_cl |> 
  mutate(
    migr_both = 
      case_when(
        w2ba0201==0 & w2ba0202==0 ~ 1,
        migr == 0 ~ 0,
        .default = NA
      )
  )
```

## Descriptive statistics
```{r Cleaned data}
df <- d_cl |>
  select(
  migr, migr_mo_only, migr_fa_only, migr_both, schids, ctyids,
  w1cog_100, w2cog_100, w1avg_100, w2avg_100, cog_dif, avg_dif,
  child.age, child.number.of.sibling, child.is.girl, child.has.rural.hukou, child.in.boarding.school, #child.had.skipped.grade, child.had.repeated.grade, 
  child.is.ethnic.minority, child.went.to.preschool, parent.has.white.collar.job, parent.expectation, parent.education.level, home.has.internet,
  child.health, child.education.aspiration, 
  #mother.education.level, father.education.level, 
  home.extracurricular.book, home.economic.resource) 
```

@@

```{r Data for treatment variable summary}
d_idpvar <- df |> 
  select(migr:migr_both) |>
  mutate(`Parental Migration` = if_else(migr==1, 'Yes', 'No')) |>
  mutate(
    `Parental Migration Type` = 
      case_when(
        migr==0 ~ 'Both Parents at Home',
        migr_mo_only==1 ~ 'Only Mother Migrated',
        migr_fa_only==1 ~ 'Only Father Migrated',
        migr_both==1 ~ 'Both Parents Migrated'
      )
) 
d_idpvar <- d_idpvar |> select(!migr & !migr_mo_only & !migr_fa_only & !migr_both)
```

```{r Treatment variable summary}
tab_idpvar <- st(
  data = d_idpvar,
  out = 'return'
)
tab_idpvar[tab_idpvar == 4204] <- ''
tab_idpvar
```

@@

```{r Data for binary control variable summary}
d_ctvar_dit <- d_migr |>
  select(`Parental Migration`,child.is.girl, child.has.rural.hukou, child.in.boarding.school,
         #child.had.skipped.grade, child.had.repeated.grade, 
         child.is.ethnic.minority, child.went.to.preschool, parent.has.white.collar.job, home.has.internet) |> 
  mutate_all(as_factor)
```

```{r Binary control variable summary}
tab_ctvar_dit <- 
  st(
  data = d_ctvar_dit,
  digits = 2,
  group = 'Parental Migration',
  group.test = list(star.cutoffs = c(0.001, 0.01, 0.05)),
  out = "return"
  )
tab_ctvar_dit <- tab_ctvar_dit[-c(1),]
tab_ctvar_dit[tab_ctvar_dit == 3529|tab_ctvar_dit == 675] <- ''
tab_ctvar_dit 
```

```{r Data for categorical control variable summary}
d_ctvar_cnt <- d_migr |>
  select(`Parental Migration`, child.age, child.number.of.sibling, child.health, child.education.aspiration, 
  parent.education.level, parent.expectation, 
  home.extracurricular.book, home.economic.resource)
```

@@

```{r Data for categorical control variable measurement}
d_ctvar_label <- d_ctvar_cnt|>
  select(!(`Parental Migration`:child.number.of.sibling)) |> 
  add_value_labels(
    parent.education.level = c(
     '0 = Primary school and below' = 0,
     '1 = Junior high school' = 1 ,
     '2 = Senior high school' = 2,
     '3 = Associate college' = 3,
     '4 = University' = 4,
     '5 = Postgraduate' = 5),
    child.education.aspiration = c(
     '0 = Does not matter' = 0,
     '1 = Junior high school' = 1,
     '2 = Senior high school' = 2,
     '3 = Associate college' = 3,
     '4 = University' = 4,
     '5 = Postgraduate' = 5),
    parent.expectation = c(
     '0 = Does not matter' = 0,
     '1 = Junior high school' = 1 ,
     '2 = Senior high school' = 2,
     '3 = Associate college' = 3,
     '4 = University' = 4,
     '5 = Postgraduate' = 5),
    home.economic.resource = c(
      '1 = Very poor' = 1,
      '2 = Somewhat poor' = 2,
      '3 = Moderate' = 3,
      '4 = Somewhat rich' = 4,
      '5 = Very rich' = 5),
    child.health = c(
      '1 = Very poor' = 1,
      '2 = Somewhat poor' = 2,
      '3 = Moderate' = 3,
      '4 = Good' = 4,
      '5 = Very good' = 5),
    home.extracurricular.book = c(
      '1 = Very few' = 1,
      '2 = Not many' = 2,
      '3 = Some' = 3,
      '4 = Quite a few' = 4,
      '5 = A great number' = 5),
    ) |>
  as_factor()
```

```{r Measurement for categorical control variable}
tab_var <- st(
  data = d_ctvar_label,
  out = 'return'
)
tab_var[tab_var == 4204] <- ''
tab_var
```

```{r Data for violin plots}
d_smr <- df |> 
  mutate(
    `Parental Migration` = 
      if_else(
        (migr==1), 'Yes', 'No')
    ) |>
  mutate(
    `Parental Migration Type` = 
      case_when(
        migr==0 ~ 'Both Parents at Home',
        migr_mo_only==1 ~ 'Only Mother Migrated',
        migr_fa_only==1 ~ 'Only Father Migrated',
        migr_both==1 ~ 'Both Parents Migrated'
      )
  )
d_smr <- d_smr |> select(!migr_mo_only & !migr_fa_only & !migr_both)
```

@@

```{r Adjusted regression on cognitive score}
did_adj_cog <- feols(cog_dif ~ migr + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df) 
did_adj_cog_m_only <- feols(cog_dif ~ migr_mo_only + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df) 
did_adj_cog_f_only <- feols(cog_dif ~ migr_fa_only + w1cog_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df) 
did_adj_cog_both <- feols(cog_dif ~ migr_both + w1cog_100  + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book  + home.has.internet | schids, data = df)
```

```{r Adjusted regression on exam grade}
did_adj_ttl <- feols(avg_dif ~ migr + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df) 
did_adj_ttl_m_only <- feols(avg_dif ~ migr_mo_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df) 
did_adj_ttl_f_only <- feols(avg_dif ~ migr_fa_only + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df) 
did_adj_ttl_both <- feols(avg_dif ~ migr_both + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.education.aspiration + child.is.ethnic.minority + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet | schids, data = df)
```

@@

## Matching
```{r Match on any parent migration}
m.out <- matchit(
  migr ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = df, 
  method = "full", 
  distance = "glm"
  )
```

@@

```{r Match on mother-only migration}
d_mo_only <- d_cl |> drop_na(migr_mo_only)
m.out_mo_only <- 
  matchit(migr_mo_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_mo_only, 
  method = "full",
  distance = "glm"
  )
```

@@

```{r Match on father-only migration}
d_fa_only <- d_cl |> drop_na(migr_fa_only)
m.out_fa_only <- matchit(
  migr_fa_only ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + parent.education.level + home.economic.resource + home.extracurricular.book + home.has.internet,
  data = d_fa_only,
  method = "full",
  distance = "glm"
  )
```

@@

```{r Match on both parents migration}
d_both <- d_cl |> drop_na(migr_both) 
m.out_both <- matchit(
  migr_both ~ w1cog_100 + w1avg_100 + child.age + child.is.girl + child.health + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.in.boarding.school + child.is.ethnic.minority + child.education.aspiration + parent.expectation + parent.has.white.collar.job + parent.education.level +  home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_both, 
  method = "full",
  distance = "glm"
  )
```

@@

```{r}
summary(m.out)
summary(m.out_mo_only)
summary(m.out_fa_only)
summary(m.out_both)
```

@@

```{}
table_m_cog
table_m_ttl
table_m_adj_cog
table_m_adj_ttl
```

```{ save image}
save.image('.RData')
```
